\chapter{Risks}
\section{Risk Managment}
For this project, the ”Project Management Triangle” is lacking the cost dimension, while the time dimension is fixed (strict deadlines). As a result, any risks that appear, automatically lead to a reduction of the project scope if there is no spare time. Because of this, we will prioritize dealing with risks above regular tasks and prioritize essential tasks over nice-to-haves, but we do not intend on planning in a flat time margin as we have no way to negotiate for more time.

\section{Estimated Risks}

\subparagraph{General Risks}
\begin{itemize}
    \item Finding Testing Participants (severity: medium, probability: high)\\ 
    \textbf{Mitigations:} Early looking for backup person \\ 
    \textbf{Actions taken:} Found backup person\\ 
    \textbf{New probability:} low
    \item Being able to create reverseable Programs with additional difficulties. (severity: very high, probability: medium)\\ 
    \textbf{Mitigations:} being able to ask Ivan \\ 
    \textbf{Actions taken:} Asked for possible help\\ 
    \textbf{New probability:} low
    \item Irreparable corruption of git server. (severity: very high, probability: low)\\ 
    \textbf{Mitigations:} Weekly off-site git server backups\\
    \textbf{Actions taken:} Repository mirrored to GitHub\\ 
    \textbf{New severity:} low
    \item Irreparable corruption of git server. (severity: very high, probability: low)\\ 
    \textbf{Mitigations:} Weekly off-site git server backups\\
    \textbf{Actions taken:} Repository mirrored to GitHub\\ 
    \textbf{New severity:} low
    \item Lost work due to un-pushed work. (severity: low, probability: high)\\ 
    \textbf{Mitigations:} Frequent reminders to push changes by Scrum Master / Team\\
\end{itemize}
\subparagraph{License Complications}
\begin{itemize}
    \item License Problems with Ghidra. (severity: high, probability: very low)\\ 
    \textbf{Mitigations:} No mitigations needed because it's completely Open Source.
    \item License Problems with IDA. (severity: high, probability: low)\\ 
    \textbf{Mitigations:} Providing a previously free version
\end{itemize}