\newglossaryentry{ida-freeware}
{
        name=IDA Freeware,
        description={Free version of IDA with same base functionalities.}
}

\newglossaryentry{radare2}
{
        name=radare2,
        description={Framework for reverse engineering usable from the command line.}
}

\newglossaryentry{hopper}
{
        name=hopper,
        description={Payed tool which allows disassembling, decompiling and debugging.}
}

\newglossaryentry{ghidra}
{
        name=ghidra,
        description={Free to use and developed by the NSA decompiling tool.}
}

\newglossaryentry{domain}
{
        name=domain,
        description={Everything that is needed for reverse engineering.}
}

\newglossaryentry{poc}
{
        name=proof of concept,
        description={Evidence obtained froma a pilot project, that the idea is feasible.}
}

\newglossaryentry{binary}
{
        name=binary,
        description={A flag is a string of text which needs to be entered into the website to show that you have solved the lab.}
}

\newglossaryentry{flag}
{
        name=flag,
        description={A pre-compiled, pre-linked program that is ready to run under a given operating system; a binary for one operating system will not run on a different operating system.}
}

\newglossaryentry{docker}
{
        name=docker,
        description={Open source platform for building, deploying, and managing containerized applications.}
}
open source platform for building, deploying, and managing containerized applications.
% --------- ACRONYMS ---------- %

\newacronym{ida}{IDA}{Interactive Disassembler}
\newacronym{aslr}{ASLR}{Address space layout randomization}
\newacronym{dep}{DEP}{Data execution prevention}
\newacronym{asm}{ASM}{Assembly Language}
\newacronym{ost}{OST}{Ostschweizer Fachhochschule}
\newacronym{gdb}{GDB}{GNU Project Debugger}Graphical user interface
\newacronym{gui}{GUI}{Graphical user interface}
\newacronym{aes}{AES}{Advanced Encryption Standard}
\newacronym{ecb}{ECB}{Electronic Code Book version of AES}
\newacronym{ects}{ECTS}{European Credit Transfer System}
\newacronym{rup}{RUP}{Rational Unified Process}
